\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-16 experience.tex
Small change.

\emph{Azure Service Fabric}\footnote{\url{http://azure.microsoft.com/en-gb/campaigns/service-fabric/}} (or \emph{Fabric} for short) is a platform and API for creating reliable services that execute on a cluster of machines. 
%The developer writes a service that receives requests (e.g.\ from some client program via HTTP requests) and mutates its state based on these requests. 
In order to make the user-written service \emph{reliable}, Fabric launches several copies (\emph{replicas}) of the service, where each copy runs as a separate process on a different node in the cluster.
%\PTComment{Cut: description of primary and secondaries, and electing a new primary.}
%One replica is selected to be the \emph{primary} which serves client requests; the rest are \emph{secondaries}. The primary replicates state changes to the secondaries by sending \emph{replication requests} so that all replicas eventually have the same state. If the primary fails (e.g.\ if the node on which the primary is running crashes), Fabric elects one of the secondaries to be the new primary and launches another secondary; the new secondary will receive a full or partial copy (depending on whether persistent storage is used) of the state of the new primary in order to ``catch up'' with the other secondaries. Fabric provides a name-resolution service so that clients can always find the current primary.
The state of the service is replicated from the \emph{primary} replica to the other \emph{secondary} replicas for redundancy.
Since user-written Fabric services are complex asynchronous and distributed applications, 
they are challenging to test.
% They are interesting targets for systematic testing with \psharp{}.

Our primary goal was to create a \psharp{} model of Fabric to allow
thorough testing of services, where Fabric's asynchrony is controlled 
by the \psharp{} runtime.
The model is written once
to include all behaviours of Fabric
so that it can be used again and again to test arbitrary Fabric services.
This was the largest among the case studies
and required multiple rounds of debugging.
The availability of systematic testing
allowed us to debug the model to
a point where reported assertion violations indicate a bug in the
user service.
Without systematic testing,
even bugs in the model would have been hard to find.
Note that we model the lowest Fabric API layer (\texttt{Fabric.dll})
which is not documented for use externally.
Eventually, we will lift the model
to higher layers
but, for this paper, we study internally-developed services
that directly target the the lowest layer.

>>>>

\emph{Azure Service Fabric}\footnote{\url{http://azure.microsoft.com/en-gb/campaigns/service-fabric/}} (or \emph{Fabric} for short) is a platform and API for creating reliable services that execute on a cluster of machines. 
%The developer writes a service that receives requests (e.g.\ from some client program via HTTP requests) and mutates its state based on these requests. 
In order to make the user-written service \emph{reliable}, Fabric launches several \emph{replicas} (copies) of the service, where each replica runs as a separate process on a different node in the cluster.
%\PTComment{Cut: description of primary and secondaries, and electing a new primary.}
%One replica is selected to be the \emph{primary} which serves client requests; the rest are \emph{secondaries}. The primary replicates state changes to the secondaries by sending \emph{replication requests} so that all replicas eventually have the same state. If the primary fails (e.g.\ if the node on which the primary is running crashes), Fabric elects one of the secondaries to be the new primary and launches another secondary; the new secondary will receive a full or partial copy (depending on whether persistent storage is used) of the state of the new primary in order to ``catch up'' with the other secondaries. Fabric provides a name-resolution service so that clients can always find the current primary.
The state of the service is replicated from the \emph{primary} replica to the other \emph{secondary} replicas for redundancy.
Since user-written Fabric services are complex asynchronous and distributed applications, 
they are challenging to test.
% They are interesting targets for systematic testing with \psharp{}.

Our primary goal was to create a \psharp{} model of Fabric to allow
thorough testing of services, where Fabric's asynchrony is controlled 
by the \psharp{} runtime.
The model is written once
to include all behaviours of Fabric
so that it can be used again and again to test arbitrary Fabric services.
This was the largest among the case studies
and required multiple rounds of debugging.
The availability of systematic testing
allowed us to debug the model to
a point where reported assertion violations indicate a bug in the
user service.
Without systematic testing,
even bugs in the model would have been hard to find.
Note that we model the lowest Fabric API layer (\texttt{Fabric.dll})
which is not documented for use externally.
Eventually, we will lift the model
to higher layers
but for this paper we study internally-developed services
that directly target the the lowest layer.
